\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSkills}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemExperience}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingEducation}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    %   \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemSkills}[2]{\resumeItemSkills{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListStartSkillsAwards}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
    \centerline{\textbf{\huge Michael Tu}}\vspace{0.15cm}
    \centerline{Email : \href{mailto:}{mtu4172@gmail.com} $|$
    Mobile : 813-474-8289 $|$
    GitHub : \href{http://github.com/mtu4172}{mtu4172} $|$
    LinkedIn : \href{http://linkedin.com/in/mtu4172}{mtu4172}}
% \end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {B.S in Computer Science; GPA: 3.95/4.00}{Aug 2021 -- May 2025}
    \resumeItemListStart
        \resumeItem{Relevant Coursework}
            {Data Structures and Algorithms, 
            Software Engineering, 
            Linear Algebra, 
            Discrete Mathematics, 
            Statistics, 
            Programming Fundamentals I/II, 
            Computer Organization
            }
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {Teaching Assistant: COP3502C - Programming Fundamentals I}{Aug 2022 -- Present}
      \resumeItemListStart
        \resumeItemExperience
          {Conducted office hours and gave weekly lectures to students enrolled in introductory Python programming course.}
        \resumeItemExperience
          {Aided instructor in grading and providing feedback on student coursework including exams, labs, and projects.}
        \resumeItemExperience
          {Helped develop course content, including programming projects, instructional materials, and study guides.}
        \resumeItemListEnd
      \resumeSubheading
      {Lockheed Martin}{Dallas, TX}
      {Incoming Software Engineering Intern}{June 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItemExperience
          {Will be working on an agile team to develop embedded software and design mission-critical software solutions.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
    % \resumeSubHeadingListStart
        \resumeSubheadingProject
          {WordHunt Solver}{Oct 2022}
          \resumeItemListStart
            \resumeItemExperience
              {Wrote a C++ app to solve the popular iMessage word puzzle game WordHunt.}
            \resumeItemExperience
              {Implemented a backtracking algorithm to find words hidden in a 2D character array. Used a Trie data structure to store dictionary and validate candidate words.}
          \resumeItemListEnd
        \resumeSubheadingProject
          {Minesweeper}{April 2022}
          \resumeItemListStart
            \resumeItemExperience
              {Built a C++ app emulating the classic puzzle game, with added functionality including toggleable debug mode.}
            \resumeItemExperience
              {Utilized Simple Fast Multimedia Library (SFML) API to support graphics and UI.}
          \resumeItemListEnd
          \resumeSubheadingProject
          {Database Research Project}{Feb 2021 -- May 2021}
          \resumeItemListStart
            \resumeItemExperience
              {Investigated the relationship between query size on relational database performance, comparing speed of full table and index scans. Both clustered and non-clustered indexes stored in B+ trees were tested.}
            \resumeItemExperience
              {Used Microsoft SQL Server and T-SQL to evaluate performance on TPC-H benchmark.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-----------Activities-----------------
\section{Involvement}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Filipino Student Association (FSA)}{Gainesville, FL}
        {Multimedia Chair}{June 2022 -- April 2023}
        \resumeItemListStart
          \resumeItemExperience
            {Produced videos promoting Filipino culture, dance, and on-campus activities using Adobe After Effects.}
          \resumeItemExperience
            {Collaborated with fellow board members to plan and organize social events for 300+ students.}
          \resumeItemExperience
            {Aided in running first-year involvement program, held meetings to guide students through the process of producing communicative media.}
        \resumeItemListEnd
      \resumeSubheading
        {HackGT 8 CTF Challenge}{Atlanta, GA}
        {Participant, Rank 16/88}{Oct 2021}
        \resumeItemListStart
          \resumeItemExperience
            {Applied knowledge of cybersecurity concepts including cryptography, web exploitation, and reverse engineering to solve challenges for hidden flags.}
             \resumeItemExperience
            {Learned to identify software vulnerabilities and use technologies such as SSH and Wireshark.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
          
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStartSkillsAwards
   \resumeSubItemSkills{Languages}{(Proficient) C++, Python, Java, MATLAB; (Familiar) SQL, JavaScript, R, ARM Assembly}
 \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards}
  \resumeSubHeadingListStartSkillsAwards
    \resumeSubItemSkills{National Merit Finalist}
      {Scored within the 99th percentile on the PSAT}
    \resumeSubItemSkills{University of Florida Dean's List}
      {College of Liberal Arts and Sciences (Fall 2021 - Spring 2023)}
  \resumeSubHeadingListEnd
  
\end{document}
